You can be Shakespeare! \\ A Case Study in Paraphrase Targeting Writing Styles

### 2012-08-24 paper/paper.tex
more writing progress..

\section{Data}
We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.

\subsection{Modern Translations}
We propose to use Shakespeare's plays and their modern English translations as a testbed for the task of paraphrasing while targeting a specific writing style.  Having access to parallel text in the target
style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation using BLEU which requires access to a set of reference translations.  For this purpose
we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us
two reference translations for 8 out of the 17 plays.

@@

\subsection{Dictionaries}

\subsection{Out of Domain Monolingual Parallel Data}

@@

\begin{comment}
\begin{itemize}
  \item Motivate the need for a benchmark dataset for evaluating the writing style paraphrase task
  \item Present Shakespeare / Modern translation data as a situation where we have parallel data available (useful for building models \& evaluating automatic evaluation metrics)
\end{itemize}
\end{comment}

>>>>

\section{Data}
We propose to use Shakespeare's plays as a testbed for the task of paraphrasing while targeting a specific writing style.  Because these plays are some of the
highest regarded examples of English literature and are also very unique in style, many linguistic resources are available such as parallel corpora
of modern translations and dictionaries of stylistically representative words and their modern equivelants.

We compare 3 different stylisitic paraphrase systems targeting Shakesperean English.  One which leverages parallel corpora of modern translations, another which makes use
of dictionaries of styalistically representative expressions, and another which leverages out-of-domain monolingual parallel data.

\subsection{Modern Translations}
Having access to parallel text in the target style allows us to train statistical models for generating paraphrases, and also perform automatic evaluation of semantic adequacy using BLEU, which requires access to a set of reference translations.  For this purpose we scraped modern translations of 17 Shakespeare plays from \url{http://nfs.sparknotes.com}, and an additional 8 translations of overlapping plays from \url{http://enotes.com}, giving us two reference translations for 8 out of the 17 plays.

@@

@@

\subsection{Baselines}
Phrase-based translation has been demonstrated to be an effective approach to generating paraphrses \cite{chen11,quirk04}, however this approach does require the existence of
parallel corpora which may not be available for many writing styles.  For this reason we were motivated to investigate alternative approaches.

\subsubsection{Dictionary Based Paraphrase}
Several dictionaries of stylistically representative words of Shakesperean English and their modern equivelants are available on the web.  These dictionaries can be used 
to define a translation model which is used in combination with a language model as in standard phrase-based MT \cite{knight}.

We gathered a set of 2,386  dictionary entries which were scraped from \url{http:/www.william-shakespeare.info} and semi-automaticaly cleaned.  Example
dictionary entries are presented in table \ref{dictionary_example}.

{\bf TODO:} need to describe how parameters were learned and combined with LM

\begin{table}
  \begin{center}
  \begin{tabular}{|l|l||l|l|}
    \hline
    target & source & target & source \\
    \hline
    \hline
    ABATE & shorten & ANIGHT & by night \\
    \hline
    CAUTEL & deceit & CHILDING & pregnant \\
    \hline
    FOIL & defeat & MORTAL & deadly \\
    \hline
  \end{tabular}
  \end{center}
  \caption{Exaple dictionary entries}
  \label{dictionary_example}
\end{table}

\subsubsection{Out of Domain Monolingual Parallel Data}

\subsection{Initial Comparison}
\begin{itemize}
  \item List the various systems we evaluate (e.g. varying LM size, etc...)
  \item Plot BLEU and PINC scores for the various systems
\end{itemize}
